### 2008-03-01 SAiP/Module1/H3/doc/softwarearchitecture.tex
Adding fixme and question 2 begin

\subsection{Question 1}
\begin{quote}
\emph{Outline how you would approach the tasks of creating the
architecture for the Beer Web Store. Consider, e.g., which steps
would you takes and in which order?}
\end{quote}

@@

\begin{quote}
\emph{Give concrete examples of what elements, relations, and structures as defined in
\cite{bass2003sa} could be in relation to an architecture for the Beer Web Store.}
\end{quote}

\begin{itemize}
    \item Relate the definition of 'software architecture' in [Bass et
    al., 2003] to the elements of your design as outlined above. Give
    concrete examples of elements, relations, and structures.
    \item Apply [Perry and Wolf, 1992]'s model of software architecture as
      \begin{quote}
	{\it Software Architecture = \{Elements, Form, Rationale\}}
      \end{quote}
      to the Beer Web System
    \item Reflect on what happens if the words ``software'' and
    ``computing'' are removed from the definition of 'software
    architecture' in [Bass et al., 2003]
    \item The architect decides to create a full architecture
    description before embarking on any implementation of the
    system. Discuss pros and cons of taking that approach
\end{itemize}

>>>>

\subsection{Question 1}
\begin{question}
Outline how you would approach the tasks of creating the
architecture for the Beer Web Store. Consider, e.g., which steps
would you takes and in which order?
\end{question}

@@

\begin{question}
Give concrete examples of what elements, relations, and structures as defined in \cite{bass2003sa} could be in relation to an architecture for the Beer Web Store.
\end{question}
\subsubsection{Elements}
Based on the present decomposition the elements that are know the layers, where each layer is an element as described below.
\begin{itemize}
    \item[Clients] The clients access the server inorder to perform some action
    \item[Server] The server is accessed by the clients and when needed access the database via its Fa\c cade pattern.
    \item[Database] The database exposes its interface to the server via a Fa\c cade pattern.
\end{itemize}
\fixme{Insert element (class) diagram for the above}
\subsubsection{Relations}
\subsubsection{Strustures}
\subsection{Question 3}
\begin{question}
\emph{Apply \cite{perrywolf1992}'s model of software architecture as
      \begin{quote}
	{\it Software Architecture = \{Elements, Form, Rationale\}}
      \end{quote}
      to the Beer Web System}
\end{question}

\begin{itemize}
    \item Apply [Perry and Wolf, 1992]'s model of software architecture as
      \begin{quote}
	{\it Software Architecture = \{Elements, Form, Rationale\}}
      \end{quote}
      to the Beer Web System
    \item Reflect on what happens if the words ``software'' and
    ``computing'' are removed from the definition of 'software
    architecture' in [Bass et al., 2003]
    \item The architect decides to create a full architecture
    description before embarking on any implementation of the
    system. Discuss pros and cons of taking that approach
\end{itemize}
